Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/evaluation.tex
Update F1 score for neuroproof.
Half-way through results.

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}? \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}
\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

>>>>

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}

\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

### 2016-11-15 paper/method.tex
Half-way through results.

\paragraph{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous. However, in reality, the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself. Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers. We explored different architectural configurations---including residual networks~\cite{resnet}---by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).

@@

\begin{figure}[t]
\centering  
\includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

>>>>

\paragraph{CNN Architecture.} Boundary split error detection is a binary classification task since the boundary is either correct or erroneous. However, in reality, the score $p$ is between 0 and 1. In connectromics, classification complexity arises from hundreds of different cell types, rather than from the classification decision itself. Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers. We explored different architectures---including residual networks~\cite{resnet}---with brute force parameter searches and precision and recall comparisons (see supplementary materials). Our final CNN configuration for split error detection has four convolutional layers, each followed by max pooling with dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\end{center}
 % \vspace{-4mm}
   \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

### 2016-11-15 paper/results.tex
Half-way through results.

We compare guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

\begin{table}[t]
\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
 & Precision & Recall & F1 score & \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Again, guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).

\begin{table}[t]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
& Precision & Recall & F1 score & \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prac4}
\end{table}

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (both provided by Haehn~\etal). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations relative to ground truth. The median VI of the initial segmentation was $0.476$ ($SD=0.089$), mean VI was $0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$ of them with an average time of $4.9$ seconds spent per correction. Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$ in $6.2$ seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier. Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.

\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases. With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$). With guided proofreading, the median VI was $0.396$ ($SD=0.032$) as shown in Fig.~\ref{fig:ac4boxplot}.

\paragraph{Subjective responses.} All subjective responses were recorded using the NASA-TLX workload index. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is not surprising since the user interface was the same for both control groups.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches. The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure}
\subsection{Automatic Error Correction}

>>>>

We compare guided and focused proofreading classifiers and report precision, recall, and F1 scores across datasets.

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Table \ref{tab:prcyl}). Our method exhibits higher precision and recall for correct and erroroneous patches.

\begin{table}[t]
\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
 & Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).

\begin{table}[t]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
& Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prac4}
\end{table}

\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches. The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure*}

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations. Median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$, with an average time of $4.9$ seconds per correction. Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average per correction time of $6.2$ seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier. %Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.

\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases. With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$). With guided proofreading, the median VI was $0.396$ ($SD=0.032$, Fig.~\ref{fig:ac4boxplot}).

\paragraph{Subjective responses.} We used the NASA-TLX workload index to record subjective responses. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is unsurprising as the user interface was the same for both groups.

\subsection{Automatic Error Correction}
